Perturbing SU($n$)-symmetric interactions

### 2019-11-08 collective_sun/sun_perturbation.tex
some changes to notation

\newcommand{\FS}{\text{FS}}

@@

To compute the effective Hamiltonian induced by the single-body
perturbation $\V_1$, we expand
\begin{align}
  H_1^{(1)} = \v v \c \P_0 \v V \P_0,
\end{align}
and use the permutational symmetry of the ground-state manifold to
simplify
\begin{align}
  H_1^{(1)} =  \sum_p v_p \P_0 V_0 \P_0 \simeq \bar v V,
  &&
  \bar v \equiv \EE_p\sp{v_p} = \f1N \sum_p v_p,
  &&
  V \equiv \sum_p V_p,
  \label{eq:H_1_1}
\end{align}
where $\simeq$ denotes equality up to a restriction to the
ground-state manifold $\M_0$, and $\EE_p\sp{x_p}$ denotes the mean
value of $x_p$.  In order to compute the second order effective
Hamiltonian $H_1^{(2)}$, we first choose an arbitrary fully symmetric
state $\ket\psi\in\M_0$ and expand (see Appendix \ref{sec:H_V1_psi}):
\begin{align}
  H_0 \V_1 \ket\psi
  = E_0 \V_1 \ket\psi
  + \p{\v v\c\m h - \v v\oc\v h}\c \v V \ket\psi,
  \label{eq:H_V1_psi_start}
\end{align}
where $\m h$ is a matrix of all coefficients $h_{pq}$ of the
interaction Hamiltonian $H_0$ in \eqref{eq:ints}; $\v h$ is a vector
of the net interaction energies $h_p\equiv\sum_qh_{pq}$ associated
with individual spins $p$; and $\v v\oc\v h$ is the element-wise
(Hadamard) product of $\v v$ and $\v h$, i.e.~a vector with components
$v_kh_k$.  We thus find that the vector $\V_1\ket\psi$ is an
eigenvector of the interaction Hamiltonian $H_0$ if the coefficients
$\v v$ satisfy
\begin{align}
  \m h \c \v v - \v h\oc\v v
  = \p{\m h - \diag\v h}\c\v v
  = \Delta\p{\v v} \v v,
  \label{eq:cond_1}
\end{align}
where $\diag\v h$ is a matrix with $\v h$ on the diagonal and zeroes
everywhere else; and $\Delta\p{\v v}$ is some constant that may depend
on $\v v$.  If the interaction Hamiltonian $H_0$ is translationally
invariant, then all $h_p=h\equiv\EE_q\sp{h_q}$ and
$\v h\oc\v v=h\v v$, so the condition in \eqref{eq:cond_1} simplifies
to
\begin{align}
  \m h \c\v v = \sp{\Delta\p{\v v}+h} \v v.
\end{align}
If we {\it construct} a perturbation $\V_1\p{\v v_\Delta}$ with
coefficients $\v v_\Delta$ that satisfy \eqref{eq:cond_1} with
eigenvalue $\Delta$, then
\begin{align}
  H_0 \V_1\p{\v v_\Delta} \ket\psi
  = \p{E_0 + \Delta} \V_1\p{\v v_\Delta} \ket\psi.
  \label{eq:H_V1_psi}
\end{align}
Interestingly, the energy of the (unnormalized) state
$\V_1\p{\v v_\Delta}\ket\psi$ depends only on the coefficients
$\v v_\Delta$, and is entirely independent of the state $\ket\psi$ or
choice of single-spin trace-zero operator $V_p$ used to build $\V_1$
in \eqref{eq:perturbations}.  Finding operators $\V_1\p{\v v_\Delta}$
that generate eigenvectors of the interaction Hamiltonian $H_0$ when
they act on fully symmetric states $\ket\psi$ thus reduces to finding
eigenvectors $\v v_\Delta$ of the interaction matrix $\m h-\diag\v h$.

@@

We now return to the task of computing the second-order effective
Hamiltonian $H_1^{(2)}$.  Any coefficient vector $\v v$ can be
expanded into its projections $\v v_\Delta$ onto the eigenspace of
vectors satisfying \eqref{eq:cond_1} with eigenvalue $\Delta$,
i.e.~$\v v = \sum_\Delta \v v_\Delta$, which also allows us to expand
\begin{align}
  \V_1\p{\v v} = \sum_\Delta \V_1\p{\v v_\Delta},
\end{align}
where each operator $\V_1\p{\v v_\Delta}$ generates a state with
definite interaction energy $\Delta$ above that of the fully symmetric
manifold.  We can therefore simplify
\begin{align}
  H_1^{(2)}
  = -\P_0 \V_1\p{\v v} \E \V_1\p{\v v} \P_0
  = - \sum_{\Delta>0} \f1{\Delta}
  \P_0 \V_1\p{\v v} \P_\Delta \V_1\p{\v v} \P_0
  = - \sum_{\Delta>0} \f1{\Delta} \P_0 \V_1\p{\v v_\Delta}^2 \P_0,
\end{align}
where the product $\P_0 \V_1\p{\v v_\Delta}^2 \P_0$ is worked out in
Appendix \ref{sec:PVVP}, giving us
\begin{align}
  H_1^{(2)} \simeq \f{\tilde v}{N-1} \p{V^2 - N W},
  &&
  \tilde v \equiv \sum_{\Delta>0} \f{\var\p{\v v_\Delta}}{\Delta}.
  \label{eq:H_1_2}
\end{align}
Here $\simeq$ denotes equality up to a restriction to the fully
symmetric manifold $\M_0$, and
\begin{align}
  \var\p{\v x} \equiv \EE_p\sp{\p{x_p-\EE_q\sp{x_q}}^2}
  = \EE_p\sp{x_p^2} - \EE_q\sp{x_q}^2,
  &&
  W \equiv \sum_p V_p^2,
\end{align}
with $\EE_p\sp{x_p}\equiv\sum_px_p/N$ the mean of $\v x$.

@@

The first-order effective Hamiltonian $H_2^{(1)}$ induced on the fully
symmetric manifold $\M_0$ by the two-body perturbation $\V_2$ in
\eqref{eq:perturbations} can be computed using the permutational
symmetry of $\M_0$ (see Appendix \ref{sec:PXYP}):
\begin{align}
  H_2^{(1)}
  = \f12 \P_0 \v X\c\m w\c\v Y\P_0
  \simeq \f12 \bar w \p{\tilde Z - Z},
\end{align}
where in terms of the anti-commutator $\sp{A,B}_+\equiv AB+BA$ and
collective operators $X\equiv\sum_p X_p$ and $Y\equiv\sum_p Y_p$, we
define
\begin{align}
  \bar w \equiv {N\choose 2}^{-1} \sum_{p<q} w_{pq},
  &&
  \tilde Z \equiv \f12 \sp{X,Y}_+,
  &&
  Z \equiv \sum_p \f12 \sp{X_p, Y_p}_+.
\end{align}
In order to compute the second-order effective Hamiltonian
$H_2^{(2)}$, as before we pick an arbitrary fully symmetric state
$\ket\psi\in\M_0$ and expand (see Appendix \ref{sec:H_V2_psi})
\begin{align}
  H_0 \V_2 \ket\psi
  = E_0 \V_2 \ket\psi
  + \v X \c \p{\bar{\m h}\oc\m w + \m h\c\m w} \c \v Y \ket\psi
  - \v\1 \c \p{\m h\oc\m w} \c \v Z \ket\psi,
  \label{eq:H_V2_psi}
\end{align}
where $\v\1$ is an $N$-component vector of ones;
\begin{align}
  \bar{\m h}
  \equiv \m h - \f12\p{\v h\otimes\v\1 + \v\1\otimes\v h}
\end{align}
is a modified interaction matrix with entries $h_{pq}-\p{h_p+h_q}/2$;
and $\m x\oc\m y$ is an element-wise (Hadamard) product of $\m x$ and
$\m y$, with entries $x_{pq}y_{pq}$.  We thus find that the vector
$\V_2\ket\psi$ is an eigenvector of the interaction Hamiltonian $H_0$
if the matrix $\m w$ of all $w_{pq}$ satisfies
\begin{align}
  \bar{\m h}\oc\m w + \m h\c\m w = \f12 \Delta\p{\m w} \m w,
  \label{eq:cond_2}
\end{align}
for some constant $\Delta\p{\m w}$ that may depend on $\m w$.
Remembering that the matrices $\m h$ and $\m w$ are both symmetric
(under transposition) with zeros on the diagonal, the diagonal
components of the condition in \eqref{eq:cond_2} automatically enforce
that the last term ($\sim\v Z$) in \eqref{eq:H_V2_psi} vanishes.

@@

% The product $\P_0 \V_2\p{\m w_\Delta}^2 \P_0$ can be written in
% terms collective operators using techniques similar to those in
% Appendix \ref{sec:sym_prod}, which should yield a effective
% Hamiltonian of the form
% \begin{align}
%   H_2^{(2)} \simeq f\p{\m w_\Delta} \O\p{\v X,\v Y},
% \end{align}
% where $f\p{\m w_\Delta}$ is a scalar and $\O\p{\v X,\v Y}$ is a
% collective operator that is independent of $\m w_\Delta$.

@@

Calculating the second-order effective Hamiltonian $H_1^{(2)}$ induced
on the fully symmetric manifold $\M_0$ by the perturbation $\V_1$ in
\eqref{eq:perturbations} requires us to simplify the product
\begin{align}
  \P_0 \V_1\p{\v v}^2 \P_0
  = \sum_{p,q} v_p v_q \P_0 V_p V_q \P_0
  = \sum_p v_p^2 \P_0 V_p^2 \P_0
  + \sum_{p\ne q} v_p v_q \P_0 V_p V_q \P_0,
  \label{eq:PVVP_start}
\end{align}
where the coefficients $\v v$ satisfy \eqref{eq:cond_1} with
eigenvalue $\Delta\ne0$, which implies that $\v v$ is mean-zero.  The
first sum on the right of \eqref{eq:PVVP_start} is then
\begin{align}
  \sum_p v_p^2 \P_0 V_p^2 \P_0
  = \sum_p v_p^2 \P_0 V_0^2 \P_0
  = \var\p{\v v} \P_0 W \P_0,
  \label{eq:PVVP_eq}
\end{align}
where
\begin{align}
  \var\p{\v v} \equiv \EE_p\sp{\p{v_p-\EE_q\sp{v_q}}^2}
  = \EE_p\sp{v_p^2} - \EE_q\sp{v_q}^2,
  &&
  W \equiv \sum_p V_p^2.
\end{align}
The second sum in \eqref{eq:PVVP_start} is
\begin{align}
  \sum_{p\ne q} v_p v_q \P_0 V_p V_q \P_0
  = \sum_{p\ne q} v_p v_q \P_0 V_0 V_1 \P_0,
  \label{eq:PVVP_neq_start}
\end{align}
where the sum over coefficients in \eqref{eq:PVVP_neq_start} can be
simplified to
\begin{align}
  \sum_{p\ne q} v_p v_q
  = \sum_{p,q} v_p v_q - \sum_{p=q} v_p v_q
  = - \sum_p v_p^2 = - N \var\p{\v v}.
\end{align}
In order to simplify the product of operators in
\eqref{eq:PVVP_neq_start}, we expand
\begin{align}
  \P_0 V^2 \P_0
  = \sum_p \P_0 V_p^2 \P_0
  + \sum_{p\ne q} \P_0 V_p V_q \P_0
  = \P_0 W \P_0 + N \p{N-1} \P_0 V_0 V_1 \P_0,
  \label{eq:PVVP_neq_ops}
\end{align}
which implies that
\begin{align}
  \sum_{p\ne q} v_p v_q \P_0 V_p V_q \P_0
  = - \var\p{\v v} N \P_0 V_0 V_1 \P_0
  = -\f{\var\p{\v v}}{N-1} \P_0 \p{V^2 - W} \P_0
  \label{eq:PVVP_neq}
\end{align}
Altogether, we have that
\begin{align}
  \P_0 \V_1\p{\v v}^2 \P_0
  = -\f{\var\p{\v v}}{N-1} \P_0 \p{V^2 - N W} \P_0,
\end{align}

@@

Calculating the first-order effective Hamiltonian $H_2^{(1)}$ induced
on the fully symmetric manifold $\M_0$ by the perturbation $\V_2$ in
\eqref{eq:perturbations} requires us to simplify the product
\begin{align}
  \P_0 \V_2 \P_0
  = \f12 \sum_{p\ne q} w_{pq} \P_0 X_p Y_q \P_0
  = {N\choose 2} \bar w \P_0 X_0 Y_1 \P_0,
  \label{eq:PXYP_start}
\end{align}
where ${N\choose2}=N\p{N-1}/2$ and
\begin{align}
  \bar w \equiv {N\choose 2}^{-1} \sum_{p<q} w_{pq}
\end{align}
is the mean value of the pair-wise couplings in $\V_2$.  To simplify
the operator content of \eqref{eq:PXYP_start}, we define
\begin{align}
  X \equiv \sum_p X_p,
  &&
  Y \equiv \sum_p Y_p,
  &&
  Z_p \equiv \f12\sp{X_p, Y_p}_+,
  &&
  Z \equiv \sum_p Z_p,
  &&
  \tilde Z \equiv \f12 \sp{X, Y}_+,
\end{align}
and expand
\begin{align}
  \P_0 \tilde Z \P_0 = \P_0 Z \P_0 + N\p{N-1} \P_0 X_0 Y_1 \P_0.
\end{align}
Substituting the product $\P_0 X_0 Y_1 \P_0$ back into
\eqref{eq:PXYP_start}, we thus find that
\begin{align}
  \P_0 \V_2 \P_0 = \f12 \bar w \P_0 \p{\tilde Z -  Z } \P_0.
\end{align}

>>>>

\newcommand{\FS}{\text{FS}}
\newcommand{\FSEQ}{=_{\text{FS}}}

@@

To compute the effective Hamiltonian induced by the single-body
perturbation $\V_1$, we use the permutational symmetry of the
ground-state manifold to simplify
\begin{align}
  H_1^{(1)} = \sum_p v_p \P_0 V_p \P_0
  = \sum_p v_p \P_0 V_0 \P_0 \FSEQ \bar v V,
  \label{eq:H_1_1}
\end{align}
where $\FSEQ$ denotes equality under a restriction to the fully
symmetric manifold $\M_0$, and
\begin{align}
  \bar v \equiv \f1N \sum_p v_p,
  &&
  V \equiv \sum_p V_p.
\end{align}
In order to compute the second order effective Hamiltonian
$H_1^{(2)}$, we first choose an arbitrary fully symmetric state
$\ket\psi\in\M_0$ and expand (see Appendix \ref{sec:H_V1_psi}):
\begin{align}
  H_0 \V_1 \ket\psi
  = E_0 \V_1 \ket\psi
  + \p{\v v\c\m h - \v v\oc\v h}\c \v V \ket\psi,
  \label{eq:H_V1_psi_start}
\end{align}
where $\m h$ is a matrix of all coefficients $h_{pq}$ of the
interaction Hamiltonian $H_0$ in \eqref{eq:ints}; $\v h$ is a vector
of the net interaction energies $h_p\equiv\sum_qh_{pq}$ associated
with individual spins $p$; and $\v v\oc\v h$ is the element-wise
(Hadamard) product of $\v v$ and $\v h$, i.e.~a vector with components
$v_kh_k$.  We thus find that the vector $\V_1\ket\psi$ is an
eigenvector of the interaction Hamiltonian $H_0$ if the coefficients
$\v v$ satisfy
\begin{align}
  \m h \c \v v - \v h\oc\v v
  = \p{\m h - \diag\v h}\c\v v
  = \Delta\p{\v v} \v v,
  \label{eq:cond_1}
\end{align}
where $\diag\v h$ is a matrix with $\v h$ on the diagonal and zeroes
everywhere else; and $\Delta\p{\v v}$ is some constant that may depend
on $\v v$.  If the interaction Hamiltonian $H_0$ is translationally
invariant, then all $h_p=h\equiv\EE_q\sp{h_q}$ and
$\v h\oc\v v=h\v v$, so the condition in \eqref{eq:cond_1} simplifies
to
\begin{align}
  \m h \c\v v = \sp{\Delta\p{\v v}+h} \v v.
\end{align}
If we {\it construct} a perturbation $\V_1\p{\v v_\Delta}$ with
coefficients $\v v_\Delta$ that satisfy \eqref{eq:cond_1} with
eigenvalue $\Delta$, then
\begin{align}
  H_0 \V_1\p{\v v_\Delta} \ket\psi
  = \p{E_0 + \Delta} \V_1\p{\v v_\Delta} \ket\psi.
  \label{eq:H_V1_psi}
\end{align}
Interestingly, the energy of the (unnormalized) state
$\V_1\p{\v v_\Delta}\ket\psi$ depends only on the coefficients
$\v v_\Delta$, and is entirely independent of the state $\ket\psi$ or
choice of single-spin trace-zero operator $V_p$ used to build $\V_1$
in \eqref{eq:perturbations}.  Finding operators $\V_1\p{\v v_\Delta}$
that generate eigenvectors of the interaction Hamiltonian $H_0$ when
they act on fully symmetric states $\ket\psi$ thus reduces to finding
eigenvectors $\v v_\Delta$ of the interaction matrix $\m h-\diag\v h$.

@@

We now return to the task of computing the second-order effective
Hamiltonian $H_1^{(2)}$.  Any coefficient vector $\v v$ can be
expanded into its projections $\v v_\Delta$ onto the eigenspace of
vectors satisfying \eqref{eq:cond_1} with eigenvalue $\Delta$,
i.e.~$\v v = \sum_\Delta \v v_\Delta$, which also allows us to expand
\begin{align}
  \V_1\p{\v v} = \sum_\Delta \V_1\p{\v v_\Delta},
\end{align}
where each operator $\V_1\p{\v v_\Delta}$ generates a state with
definite interaction energy $\Delta$ above that of the fully symmetric
manifold $\M_0$.  We can therefore simplify
\begin{align}
  H_1^{(2)}
  = - \P_0 \V_1\p{\v v} \E \V_1\p{\v v} \P_0
  = - \sum_{\Delta>0} \f1{\Delta}
  \P_0 \V_1\p{\v v} \P_\Delta \V_1\p{\v v} \P_0
  = - \sum_{\Delta>0} \f1{\Delta} \P_0 \V_1\p{\v v_\Delta}^2 \P_0,
\end{align}
where the product $\P_0 \V_1\p{\v v_\Delta}^2 \P_0$ is worked out in
Appendix \ref{sec:PVVP}.  In total, we find
\begin{align}
  H_1^{(2)} \FSEQ \f{\tilde v}{N-1} \p{V^2 - N W},
  &&
  \tilde v \equiv \sum_{\Delta>0} \f{\var\p{\v v_\Delta}}{\Delta},
  \label{eq:H_1_2}
\end{align}
where $\FSEQ$ denotes equality under a restriction to the fully
symmetric manifold $\M_0$, and
\begin{align}
  \var\p{\v x} \equiv \EE_p\sp{\p{x_p-\EE_q\sp{x_q}}^2}
  = \EE_p\sp{x_p^2} - \EE_q\sp{x_q}^2,
  &&
  W \equiv \sum_p V_p^2,
\end{align}
with $\EE_p\sp{x_p}\equiv\sum_px_p/N$ the mean value in $\v x$.

@@

The first-order effective Hamiltonian $H_2^{(1)}$ induced on the fully
symmetric manifold $\M_0$ by the two-body perturbation $\V_2$ in
\eqref{eq:perturbations} is simply the restriction of $\V_2$ onto
$\M_0$ (see Appendix \ref{sec:PXYP}):
\begin{align}
  H_2^{(1)}
  = \P_0 \V_2 \P_0
  \FSEQ \f12 \bar w \p{\tilde Z - Z},
\end{align}
where in terms of the anti-commutator $\sp{A,B}_+\equiv AB+BA$ and
collective operators $X\equiv\sum_p X_p$ and $Y\equiv\sum_p Y_p$, we
define
\begin{align}
  \bar w \equiv {N\choose 2}^{-1} \sum_{p<q} w_{pq},
  &&
  \tilde Z \equiv \f12 \sp{X,Y}_+,
  &&
  Z \equiv \sum_p \f12 \sp{X_p, Y_p}_+.
\end{align}
In order to compute the second-order effective Hamiltonian
$H_2^{(2)}$, as before we pick an arbitrary fully symmetric state
$\ket\psi\in\M_0$ and expand (see Appendix \ref{sec:H_V2_psi})
\begin{align}
  H_0 \V_2 \ket\psi
  = E_0 \V_2 \ket\psi
  + \v X \c \p{\bar{\m h}\oc\m w + \m h\c\m w} \c \v Y \ket\psi
  - \v\1 \c \p{\m h\oc\m w} \c \v Z \ket\psi,
  \label{eq:H_V2_psi}
\end{align}
where $\v\1$ is an $N$-component vector of ones;
\begin{align}
  \bar{\m h}
  \equiv \m h - \f12\p{\v h\otimes\v\1 + \v\1\otimes\v h}
\end{align}
is a modified interaction matrix with entries $h_{pq}-\p{h_p+h_q}/2$;
and $\m x\oc\m y$ is an element-wise (Hadamard) product of $\m x$ and
$\m y$, with entries $x_{pq}y_{pq}$.  We thus find that the vector
$\V_2\ket\psi$ is an eigenvector of the interaction Hamiltonian $H_0$
if the matrix $\m w$ of all $w_{pq}$ satisfies
\begin{align}
  \bar{\m h}\oc\m w + \m h\c\m w = \f12 \Delta\p{\m w} \m w,
  \label{eq:cond_2}
\end{align}
for some constant $\Delta\p{\m w}$ that may depend on $\m w$.
Remembering that the matrices $\m h$ and $\m w$ are both symmetric
(under transposition) with zeros on the diagonal, the diagonal
components of the condition in \eqref{eq:cond_2} automatically enforce
that the last term ($\sim\v Z$) in \eqref{eq:H_V2_psi} vanishes.

@@

@@

Calculating the second-order effective Hamiltonian $H_1^{(2)}$ induced
on the fully symmetric manifold $\M_0$ by the perturbation $\V_1$ in
\eqref{eq:perturbations} requires us to simplify
\begin{align}
  \P_0 \V_1\p{\v v}^2 \P_0
  \FSEQ \sum_{p,q} v_p v_q V_p V_q
  = \sum_p v_p^2 V_p^2
  + \sum_{p\ne q} v_p v_q V_p V_q,
  \label{eq:PVVP_start}
\end{align}
where $\FSEQ$ denotes equality under a restriction to the fully
symmetric manifold $\M_0$; and the coefficients $\v v$ satisfy
\eqref{eq:cond_1} with eigenvalue $\Delta\ne0$, which implies that
$\v v$ is mean-zero.  The first sum on the right of
\eqref{eq:PVVP_start} is then
\begin{align}
  \sum_p v_p^2 V_p^2
  \FSEQ \sum_p v_p^2 V_0^2
  \FSEQ \var\p{\v v} W,
  \label{eq:PVVP_eq}
\end{align}
where
\begin{align}
  \var\p{\v v} \equiv \EE_p\sp{\p{v_p-\EE_q\sp{v_q}}^2}
  = \EE_p\sp{v_p^2} - \EE_q\sp{v_q}^2,
  &&
  W \equiv \sum_p V_p^2.
\end{align}
The second sum on the right of \eqref{eq:PVVP_start} is
\begin{align}
  \sum_{p\ne q} v_p v_q V_p V_q
  \FSEQ \sum_{p\ne q} v_p v_q V_0 V_1,
  \label{eq:PVVP_neq_start}
\end{align}
where the sum over coefficients in \eqref{eq:PVVP_neq_start} can be
simplified to
\begin{align}
  \sum_{p\ne q} v_p v_q
  = \sum_{p,q} v_p v_q - \sum_{p=q} v_p v_q
  = - \sum_p v_p^2 = - N \var\p{\v v}.
\end{align}
In order to simplify the product of operators in
\eqref{eq:PVVP_neq_start}, we expand
\begin{align}
  V^2
  = \sum_p V_p^2
  + \sum_{p\ne q} V_p V_q
  \FSEQ W + N \p{N-1} V_0 V_1,
  \label{eq:PVVP_neq_ops}
\end{align}
which implies that
\begin{align}
  \sum_{p\ne q} v_p v_q V_p V_q
  \FSEQ - \var\p{\v v} N V_0 V_1
  \FSEQ -\f{\var\p{\v v}}{N-1} \p{V^2 - W}
  \label{eq:PVVP_neq}
\end{align}
Altogether, we have that
\begin{align}
  \V_1\p{\v v}^2
  \FSEQ -\f{\var\p{\v v}}{N-1} \p{V^2 - N W}.
\end{align}

@@

Calculating the first-order effective Hamiltonian $H_2^{(1)}$ induced
on the fully symmetric manifold $\M_0$ by the perturbation $\V_2$ in
\eqref{eq:perturbations} requires us to simplify
\begin{align}
  \P_0 \V_2 \P_0
  \FSEQ \f12 \sum_{p\ne q} w_{pq} X_p Y_q
  = {N\choose 2} \bar w X_0 Y_1,
  \label{eq:PXYP_start}
\end{align}
where $\FSEQ$ denotes equality under a restriction to the fully
symmetric manifold $\M_0$, ${N\choose2}=N\p{N-1}/2$ is a binomial
coefficient, and
\begin{align}
  \bar w \equiv {N\choose 2}^{-1} \sum_{p<q} w_{pq}
\end{align}
is the mean value of the pair-wise couplings in $\V_2$.  To simplify
the operator content of \eqref{eq:PXYP_start}, we define
\begin{align}
  X \equiv \sum_p X_p,
  &&
  Y \equiv \sum_p Y_p,
  &&
  Z_p \equiv \f12\sp{X_p, Y_p}_+,
  &&
  Z \equiv \sum_p Z_p,
  &&
  \tilde Z \equiv \f12 \sp{X, Y}_+,
\end{align}
and expand
\begin{align}
  \tilde Z \FSEQ Z + N\p{N-1} X_0 Y_1.
\end{align}
Substituting the product $X_0 Y_1$ back into \eqref{eq:PXYP_start}
gives us
\begin{align}
  \V_2 \FSEQ \f12 \bar w \p{\tilde Z -  Z }.
\end{align}
